R Notebook

### 2019-06-10 ICS_Cleaning.Rmd
matched up TB/SM/donor nomenclature

@@

l<-list(CD4_Counts.csv, CD4_Cytokine.csv, CD4_MFI.csv, CD4_new.csv,
        CD4_phenotype_new.csv, CD4_phenotype.csv, CD4.csv, 
        CD8_Counts.csv, CD8_Cytokine.csv, 
        GD_Counts.csv, GD_Cytokine.csv
        )
l<-lapply(l, function(x) clean_flowjo_output(x))
l<-lapply(l, function(x) splitter(x, "Sample", "_", one="Donor", two="TB", three="SM", four="Stim"))
l<-lapply(l, function(x) fix.names(x))
l<-lapply(l, function(x) remove_samples(x))
l<-lapply(l, function(x) remove_donors_ICS(x))
l<-lapply(l, function(x) class_change(x))
l<-lapply(l, function(x) changeTB(x))

@@

>>>>

```{r ICS compass}
ICS_Compass_scores_complete.csv<-changeTB(ICS_Compass_scores_complete.csv)
ICS_Compass_scores_complete.csv<-changeHD(ICS_Compass_scores_complete.csv)
ICS_Compass_scores_complete.csv<-fix.names(ICS_Compass_scores_complete.csv)
ICS_Compass_scores_complete.csv<-remove_samples(ICS_Compass_scores_complete.csv)
ICS_Compass_scores_complete.csv<-remove_donors(ICS_Compass_scores_complete.csv)
write.csv(ICS_Compass_scores_complete.csv,
          "/Applications/Old Computer/Day Lab/Flow-Data/clean/ICS_compass_complete_clean.csv"
)
```

@@

l<-list(CD4_Counts.csv, CD4_Cytokine.csv, CD4_MFI.csv, CD4_new.csv,
        CD4_phenotype_new.csv, CD4_phenotype.csv, CD4.csv, 
        CD8_Counts.csv, CD8_Cytokine.csv, 
        GD_Counts.csv, GD_Cytokine.csv
        )
l<-lapply(l, function(x) clean_flowjo_output(x))
l<-lapply(l, function(x) splitter(x, "Sample", "_", one="Donor", two="TB", three="SM", four="Stim"))
l<-lapply(l, function(x) fix.names(x))
l<-lapply(l, function(x) remove_samples(x))
l<-lapply(l, function(x) remove_donors(x))
l<-lapply(l, function(x) class_change(x))
l<-lapply(l, function(x) changeTB(x))
l<-lapply(l, function(x) changeHD(x))

@@

```{r remove specific CD8/GD tables}
pbmc<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/clean/ICS_DonorInfo_clean.csv")
cd8.remove<-filter(pbmc, grepl("CD8", Excluded))$Donor
CD8_Counts.csv<-filter(CD8_Counts.csv, !(Donor %in% cd8.remove))
CD8_Cytokine.csv<-filter(CD8_Cytokine.csv, !(Donor %in% cd8.remove))

gd.remove<-filter(pbmc, grepl("CD4-", Excluded))$Donor
GD_Counts.csv<-filter(GD_Counts.csv, !(Donor %in% cd8.remove))
GD_Cytokine.csv<-filter(GD_Cytokine.csv, !(Donor %in% cd8.remove))

```
